A statistically consistent approach to chemical tagging

### 2018-11-16 article/ms.tex
fix tests and add figures from toy model grid search

>>>>

\todo{Grid search text}

\begin{figure}
	\includegraphics[width=0.45\textwidth]{experiments/toy-ll-contours.png}
	\includegraphics[width=0.45\textwidth]{experiments/toy-bic-contours.png}
	\includegraphics[width=0.45\textwidth]{experiments/toy-pseudobic-contours.png}
    \caption{Model performance metrics resulting from a gridsearch using the
    		 data generated as part of our toy model. The top 
		 	 panel shows the negative log-likelihood 
			 $-\log{\mathcal{L}\left(\data|\vec\Psi\right)}$ 
			 evaluated at each combination of latent factors $J$ and number 
			 of clusters $K$, the middle panel shows the Bayesian Information
			 Criterion (Equation \ref{eq:bic}), and the lower panel shows
			 the pseudo-Bayesian Information Criterion 
			 (Equation~\ref{eq:pseudo-bic}). The white marker indicates the 
			 lowest value in each panel.}
    \label{fig:experiment-1-gridsearch}
\end{figure}
